VOI-based Monte Carlo Sampling

### 2011-09-13 paper/voisam/paper.tex
bounds

\begin{description}
\item[Markov' inequality \cite{}:] Let $X \ge 0$ be a random non-negative variable
  with finite mean $\IE[X]$. Then for all $a > 0$
\begin{equation}
\Pr(X\ge a)\le \frac {\IE[X]} a
\label{eq:conc-markov-upper}
\end{equation}
If additionally $X\le 1$, then by susbstituting $Y=1-X$
\begin{equation}
\Pr(X\le a)\le \frac {1-\IE[X]} {1-a}
\label{eq:conc-markov-lower}
\end{equation}
\item[Hoeffding's inequality \cite{}:] Let $X_1, \ldots, X_n$ be
independent random variables with values from $[0,1]$,
$X=\frac 1 n \sum_{i=1}^n X_i$. Then 
\begin{eqnarray}
\Pr(X-\IE[X] \ge a) &\le& \exp ( -2na^2)\nonumber\\
\Pr(\IE[X]-X \ge a) &\le& \exp ( -2na^2)
\label{eq:conc-hoeffding}
\end{eqnarray}
\item[Maurer \& Pontil's inequality \cite{MaurerPontil.benrstein}:] \footnote{A
  modification of Bennet's inequality \cite{} based on the sample,
  rather than the true, variance.}
\end{description}

>>>>

Let $X_1, \ldots, X_n$ be i.i.d. random variables with values from $[0,1]$,
$X=\frac 1 n \sum_{i=1}^n X_i$. Then 
\begin{description}
\item[Hoeffding's inequality \rm{\cite{Hoeffding.ineq}}:] 
\begin{equation}
\Pr(X-\IE[X] \ge a) \le \exp ( -2na^2)
\label{eq:conc-hoeffding}
\end{equation}
\item[Empirical Bernstein's inequality \rm{\cite{MaurerPontil.benrstein}}:]
\begin{equation}
\Pr(X-\IE[X] \ge a) \le 2\exp \left( \frac {-na^2} {10a+2\overline\sigma_n^2}\right)
\label{eq:conc-empbernstein}
\end{equation}
where sample variance $\overline\sigma_n^2$ is
\begin{equation}
\overline\sigma_n^2=\frac 1 {n(n-1)} \sum_{1\le i < j\le n}(X_i-X_j)^2
\label{eq:sample-variance}
\end{equation}
\end{description}
Bounds (\ref{eq:conc-hoeffding}, \ref{eq:conc-empbernstein}) are symmetrical
around the mean. Bound (\ref{eq:conc-empbernstein}) is tighter than
(\ref{eq:conc-hoeffding}) for small $a$ and $\overline\sigma_n^2$.
